Meta-analysis

### 2020-01-31 05_MetaAnalysis.Rmd
first test of lmer of AUDPC

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)
```

# Meta-analysis
## Preliminary meta-analysis

@@

slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")

@@

>>>>

library(RColorBrewer)
library(tidyverse)
library(theme.usq)
library(bomrang)
library(lme4)
library(kableExtra)

# Data
slimmer_PM_dat <- read.csv("data/slimmer_PM_clusterdat.csv")
```

# Meta-analysis
## Grain yield meta-analysis

@@

@@

## AUPDC and PM severity meta-analysis

```{r LMER_AUDPC}

Me_mod1 <- lmer(grain_yield.t.ha ~ AUDPC_m + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod1)

Me_mod2 <- lmer(grain_yield.t.ha ~ AUDPC_m + (AUDPC_m|trial),
              data = slimmer_PM_dat)
summary(Me_mod2)

anova(Me_mod1, Me_mod2)

```{r LMER_finalSev}

Me_mod3 <- lmer(grain_yield.t.ha ~ PM_final_severity + (1|trial),
              data = slimmer_PM_dat)
summary(Me_mod3)

Me_mod4 <- lmer(grain_yield.t.ha ~ PM_final_severity + (PM_final_severity|trial),
              data = slimmer_PM_dat)
summary(Me_mod4)

anova(Me_mod1, Me_mod2)
